HUME: Human UCCA-based Machine-Translation Evaluation

### 2016-03-08 paper/main.tex
more

UCCA (Universal Conceptual Cognitive Annotation) is a natural selection for purposes of MT evaluation
for a number of reasons. 
First, it diverges from the above approaches in representing
semantic structure as a hierarchy of units, defined using coarse-grained and intuitive definitions,
and consequently can be reliably annotated by non-experts, after as little as two hours
of training \cite{marinotti2014}.
Second, UCCA is a cross-linguistically applicable scheme, seeking to represent what is shared between languages,
by building on an established framework for typological description called
``Basic Linguistic Theory'' \cite[BLT]{Dixon:10a,Dixon:10b,Dixon:12},
one of the most widely used frameworks for linguistic description.
Indeed, the scheme's cross-linguistic applicability has been demonstrated through its
application to annotation in English, French, German and Czech. 
Third, the scheme has been shown to be semantically stable
in translation: UCCA annotations of translated text usually contain the same set of relationships
\cite{sulem2012}. This is an important feature for the semantic annotation, as it allows us to
assume that the semantic units of the source indeed reflect a common layer of representation that
should be preserved in translation, and so should be represented in the translation output too.
The non-stability of verbal argument structures, which may be translated to a nominal or adjectival
argument structure in another language, is one of the shortcomings of MEANT which HUME addresses.
\oa{example?}

@@

@@

\oa{add statistics about frequency of nominalization and copula clauses and linkers annotation}

\oa{what is the purpose of the BLEU binning?}

@@

>>>>

UCCA (Universal Conceptual Cognitive Annotation) is a natural pick for purposes of MT evaluation
for a number of reasons. 
First, it diverges from the above approaches in representing
semantic structure as a hierarchy of units, defined using coarse-grained and intuitive definitions,
and consequently can be reliably annotated by non-experts, after as little as two hours
of training \cite{marinotti2014}.
Second, UCCA is a cross-linguistically applicable scheme, seeking to represent what is shared between languages,
by building on an established framework for typological description called
``Basic Linguistic Theory'' \cite[BLT]{Dixon:10a,Dixon:10b,Dixon:12},
one of the most widely used frameworks for linguistic description.
Indeed, the scheme's cross-linguistic applicability has been demonstrated through its
application to annotation in English, French, German and Czech. 
Third, the scheme has been shown to be semantically stable
in translation: UCCA annotations of translated text usually contain the same set of relationships
\cite{sulem2012}. This is an important feature for the semantic annotation, as it allows us to
assume that the semantic units of the source indeed reflect a common layer of representation that
should be preserved in translation, and so should be represented in the translation output too.
The non-stability of verbal argument structures, which may be translated to a nominal or adjectival
argument structure in another language, is one of the shortcomings of MEANT which HUME addresses.

@@

\subsection{Annotation Guidelines}\label{sec:guidelines}

\subsection{Composite Score}\label{sec:score}

composite score (uniform, sub-sets, weighted rather not -- according to categories [or empirically according to agreement])

@@

We conducted an analysis of the English UCCA Wikipedia
corpus\footnote{\url{http://www.cs.huji.ac.il/~oabend/ucca.html}}, comprising
of 5324 sentences,
in order to assess the frequency of some of the major phenomena HMEANT fails to address,
Coppula cluases are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to a conservative estimates that only considers non-auxilliary instances of ``be''.
Nominative argument structures, which are completely ignored under HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences. Linkers expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified
  non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger.}.
We are not aware of any empirical evaluation that demonstrates that verb argument structure,
taken alone, capture the crux of the sentence semantics meanings, and so the coverage of
further phenomena by HUME will first allow to determine empirically
(rather than stipulate), what semantic structures are important
to preserve for MT translation, and which are less important

@@

\subsection{Data}\label{sec:data}

\subsection{Efficient of Annotation}\label{sec:efficiency}

\subsection{Agreement across Languages }\label{sec:efficiency}

\oa{what is the purpose of the BLEU binning? is it because low quality and high
quality translations often diverge in their agreement scores?}

\subsection{Discussion of Disagreements}\label{sec:disagreements}

\subsection{Comparison with Crowdsourced Adequacy Judgements}\label{sec:adequacy}
